%-------------------------
% Resume in Latex
% Author : Matty
% Based on: https://github.com/jakegut/resume (which was based on https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} 
      \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingSP}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3}\\
      \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

% -------------------- Personal Project --------------------
\section{Academic Research}
  \resumeSubHeadingListStart


        \resumeProjectHeading
        {\textbf{Retention Analysis and Inference for MOUD Treatment} $|$ \footnotesize\emph{Decision Analytics Lab}} {Jan. 2024 - Now}
        \resumeItemListStart
            \resumeItem{Conducted literature review and full data handling, from initial extraction to exploratory analysis and feature selection, for researches on Treatment Discontinuation of Opioid Use Disorder.}

            \resumeItem{Utilized causal inference and machine learning techniques to identify factors influencing opioid treatment outcomes, applying propensity score matching to mitigate bias from confounding variables.}
            \resumeItem{Developed and tested a deep learning \textbf{forecasting model} to forecast treatment discontinuations to enhance healthcare decision-making.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Operational Report on Nurse Staffing Strategy}} {March. 2024}
        \resumeItemListStart
            \resumeItem{Spearheaded the development of mathematical model to optimize nurse staffing processes, assisting with hiring decisions at a small hospital over a 12-month period.}

            \resumeItem{Implemented a strategic hiring model accommodating three nurse types (full-time, travel, and agency), integrating market constraints and hospital demand to minimize staffing costs.}
            \resumeItem{Conducted comprehensive sensitivity analysis to enhance model adaptability, ensuring robust decision-making across varying market and demand scenarios.}
        \resumeItemListEnd

                \resumeProjectHeading
        {\textbf{Database design for Boston Attractions site}} {Dec. 2023}
        \resumeItemListStart
            \resumeItem{Executed end-to-end database design for Boston Attractions Website, aimed at tourists, featuring lists of attractions and insights extracted from reviews to enhance visitor experiences.}

            \resumeItem{Implemented the database using both \textbf{MySQL and MongoDB}, and integrated it with a web application built using \textbf{Flask}, featuring a list of attractions and an interactive dashboard for data display and insights.}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Auto Insurance Risk Assessment Model on Claim Data} } {May. 2022}
        \resumeItemListStart
            \resumeItem{Developed a predictive model with a dataset of 600,000 samples to improve \textbf{auto insurance claim prediction} accuracy and boost company profits.}

            \resumeItem{Leveraged data preprocessing techninques like  under-sampling to overcome class imbalance and feature engineering to ensure model robustness.}
            \resumeItem{Utilized XGBoost for both model training and feature importance assessment, \textbf{achieving a high auto insurance claim prediction accuracy}(Gini coefficient of 0.291).}
        \resumeItemListEnd

                                \resumeProjectHeading
        {\textbf{GenAI-powered Landmark Selfie Service Startup} $|$ \footnotesize\emph{Co-founder}}{August 2023}
        \resumeItemListStart
        
            \resumeItem{Developed and launched a GenAI-powered live landmark selfie service for tourists, conducting customer research, designing marketing strategies, and optimizing workflows, resulting in weekly revenue of 4200 RMB}
            \resumeItem{Engineered \textbf{prompts and iterated on Midjourney-based workflow} to enhance AI-generated landmark selfies, building test sets to address limitations like hallucinations and \textbf{ improving output qualification rate by 90\% }}
            \resumeItem{Proposed a local special commodities project based on designed workflow to create culturally-relevant products, collaborating with the local tourism department to expand target audience and community impact}
        \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{RAG for Machine Learning Concept Learning} } {April. 2024}
        \resumeItemListStart
            \resumeItem{Developed a LLM-powered RAG question answering system focused on machine learning concepts}

            \resumeItem{Leveraged LangChain to implement end-to-end RAG solution, including prompt engineering, text preprocessing, embedding, and QA chain construction}
            \resumeItem{Developed test cases to evaluate performance of the RAG system, utilizing bad case to iteratively improve both generated outputs and retrieval quality in the RAG system}
        \resumeItemListEnd



          
    \resumeSubHeadingListEnd 



           

\end{document}
